---
title: "Some Kind of Exploratory Analysis"
subtitle: "An exploratory data anylsis of the iconic phrases 'some kind/type/sort/form of' of StarTrek, with a focus on VOY."
author: Christian Gebhard
format: html
code-fold: true
---

## Setup

```{r load packages}
#| output: false
#| code-summary: load packages
library("tidyverse")
library("rtrek")
library("trekfont")
library("showtext")
library("knitr")
library("kableExtra")
```

```{r setup fonts}
#| output: false
#| code-summary: setup fonts

# adapted from {trekfont} documentation:
fonts <- c("StarNext", "Federation", "FederationBold")
path <- system.file(paste0("fonts/", fonts, ".ttf"), package = "trekfont")
for(i in seq_along(fonts)) font_add(fonts[i], path[i])
# font_families()
showtext_auto()

```


```{r}
#| output: false
#| code-summary: read cleaned data

# data downloaded and cleaned in some-kind-of-cleaning.R
some_kind_of_df <- read_csv("some-kind-of-cleaned-data.csv")

```


## Exploratory Analysis

### What series overdoes it with these phrases?

```{r}
some_kind_of_df |> 
  group_by(series) |> 
  count(what_said) |> 
  pivot_wider(id_cols = c(series), names_from = what_said, values_from = n, values_fill = 0L) |> 
  mutate(
    any_phrase = rowSums(across(where(is.numeric)))
  ) |> 
  arrange(desc(any_phrase)) |> 
  relocate(series, any_phrase) |> 
  knitr::kable()


```

So, we have a clear winner: VOY with 353 occurrences of any of the four phrases.

:::{.callout-important collapse=false appearance='default' icon=true}
Note, that this number differs from the extensive collection in the ["Some kind of...StarTrek Supercut" Video](https://youtu.be/JwZiezIxCVU) by Jogwheel. At this point I'm unable to manually compare the dataset obtained via {rtrek} with the video. As the packages author [Matt Leonawicz](https://github.com/leonawicz) points out: 

> "The dataset is nicely curated, but imperfect. There are text-parsing edge cases that are difficult to handle generally. The quality varies substantially across series."
:::

I'll mostly work on VOY for the rest of this EDA:
```{r}
some_kind_of_VOY <- some_kind_of_df |> 
  filter(series == "VOY")
```


### Who said what most often in VOY?

```{r}
some_kind_of_VOY |> 
  group_by(character) |> 
  count(what_said, sort = T) |> 
  pivot_wider(id_cols = c(character), names_from = what_said, values_from = n, values_fill = 0L) |> 
  head(10) |> 
  knitr::kable()
```

### Is there a dynamic across the VOY seasons?

```{r}
by_season <- some_kind_of_df |> 
  group_by(season) |> 
  count(what_said) |> 
  pivot_wider(id_cols = c(season), names_from = what_said, values_from = n, values_fill = 0L) 

by_season |> knitr::kable()
```

### What episode is leading in VOY?

```{r}
by_episode <- some_kind_of_df |> 
  filter(series == "VOY") |> 
  group_by(number) |> 
  count(what_said) |> 
  arrange(number)

episode_titles <- some_kind_of_df |> 
  filter(series == "VOY") |> 
  select(number, season, title)

by_episode |>
  head(1) |> 
  left_join(episode_titles, by = "number") |> 
  distinct() |> 
  knitr::kable()
```



## Honorary Mentions

Some of the characters in other series are also playing in the first league of overused phrases. Here's how they compare to the Voyager crew:

```{r}
some_kind_of_df |> 
  group_by(character, series) |> 
  count(what_said, sort = T) |> 
  pivot_wider(id_cols = c(character, series), names_from = what_said, values_from = n, values_fill = 0L) |> 
  head(10) |> 
  ungroup() |> 
  mutate(rank = 1:10) |> 
  relocate(rank) |> 
  kable() |> 
  row_spec(c(5, 6, 8, 10), bold = T, color = "white", background = "#D7261E")
```

