---
title: "Some Kind of Exploratory Analysis"
subtitle: "An exploratory data anylsis of the iconic phrases 'some kind/type/sort/form of' of StarTrek, with a focus on VOY."
author: Christian Gebhard
format: html
code-fold: true
---

## Setup

```{r load packages}
#| output: false
#| code-summary: load packages
library("tidyverse")
library("rtrek")
library("trekfont")
library("showtext")
```

```{r setup fonts}
#| output: false
#| code-summary: setup fonts

# adapted from {trekfont} documentation:
fonts <- c("StarNext", "Federation", "FederationBold")
path <- system.file(paste0("fonts/", fonts, ".ttf"), package = "trekfont")
for(i in seq_along(fonts)) font_add(fonts[i], path[i])
# font_families()
showtext_auto()

```


```{r}
#| output: false
#| code-summary: read cleaned data

# data downloaded and cleaned in some-kind-of-cleaning.R
some_kind_of_df <- read_csv("some-kind-of-cleaned-data.csv")

```


## Exploratory Analysis

### What series overdoes it with these phrases?

```{r}
some_kind_of_df |> 
  group_by(series) |> 
  count(what_said) |> 
  pivot_wider(id_cols = c(series), names_from = what_said, values_from = n, values_fill = 0L) |> 
  mutate(
    any_phrase = rowSums(across(where(is.numeric)))
  ) |> 
  arrange(desc(any_phrase)) |> 
  relocate(series, any_phrase) |> 
  knitr::kable()


```

So, we have a clear winner: VOY with 353 occurrences of any of the four phrases.^[Note, that this number differs from the extensive collection in the ["Some kind of...StarTrek Supercut" Video](https://youtu.be/JwZiezIxCVU) by Jogwheel. At this point I'm unable to compare the dataset obtained via {rtrek} with the video. As the packages author [Matt Leonawicz](https://github.com/leonawicz) points out: "The dataset is nicely curated, but imperfect. There are text-parsing edge cases that are difficult to handle generally. The quality varies substantially across series."]

### Who said what most often?

```{r}
some_kind_of_df |> 
  group_by(character) |> 
  count(what_said, sort = T) |> 
  pivot_wider(id_cols = c(character), names_from = what_said, values_from = n, values_fill = 0L) |> 
  head(10) |> 
  knitr::kable()
```

### Is there a dynamic across the episodes / seasons?

```{r}
by_season <- some_kind_of_df |> 
  group_by(season) |> 
  count(what_said) |> 
  pivot_wider(id_cols = c(season), names_from = what_said, values_from = n, values_fill = 0L) 

by_season |> knitr::kable()
```


```{r}
by_episode <- some_kind_of_df |> 
  group_by(number) |> 
  count(what_said, sort = T)

by_episode |>
  head(10) |> 
  knitr::kable()
```



